Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-01-10 ms/ms06_floats.tex
ENH added marker gene

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=ccrrp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Cytoband & \bfseries Pos (hg38) & \bfseries Variant & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{Colocalized eQTL/GWAS variants involved in 5 or more GWAS classes. Genomic coordinates are given for the hg38 assembly. }\label{tab:pleitropic_variants}
\end{table}

>>>>

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=crclcp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker & \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{eQTLs involved in four GWAS categories. The gene marker is the eQTL gene with highest PubMed publication count.}
\label{tab:pleitropic_variants}
\end{table}
